### 2017-06-09 sheets/talk-6/sheet-6.tex
Fix typo in sample solution 6.6

\begin{answer}
  \begin{proof}
    We numerate the statements:
    \begin{itemize}
      \item  [I:]$s=t$
      \item [II:]The qualizer of $s$ and $t$ exists and is an isomorphism.
      \item[III:]The coequalizer of $s$ and $t$ exists and is an isomorphism.
    \end{itemize}
    We show that all statements are equivalent by showing $I \Leftrightarrow II$ and $I \Leftrightarrow III$.
    Note that $I \Leftrightarrow III$ is the dualized result of $I \Leftrightarrow II$, so we only need to show $I \Leftrightarrow II$.

@@

>>>>

\begin{answer}
  \begin{proof}
    We numerate the statements:
    \begin{itemize}
      \item  [I:]$s=t$
      \item [II:]The equalizer of $s$ and $t$ exists and is an isomorphism.
      \item[III:]The coequalizer of $s$ and $t$ exists and is an isomorphism.
    \end{itemize}
    We show that all statements are equivalent by showing $I \Leftrightarrow II$ and $I \Leftrightarrow III$.
    Note that $I \Leftrightarrow III$ is the dualized result of $I \Leftrightarrow II$, so we only need to show $I \Leftrightarrow II$.

@@

\begin{answer}
  The coequalizer follows the scheme like in the talk.
  We define the relation $R := \set{ (1_X (x), f(x) \;\big|\; x \in X} = \set{ (x, f(x) \;\big|\; x \in X} = f$ defined as a set.
  Now $\sim$ is the reflexive symmetric transitive closure of $R$.
  We define $i(x) := [x] := \set{ x' \in X | x \sim x'}$
  and the quotient $C := X / \sim \;=\; i(X)$.
  Now
  $ \xymatrix{
    X \ar@<.5ex>[r]^f \ar@<-.5ex>[r]_{1_X} & X \ar[r]^i & C
  } $
  is the coequalizer of $\parpairi{X}{X}{f}{1}$.
  The equivalence $\sim$ has the property:
  $\forall x_1, x_2 \in X, (x_1, x_2) \in \sim \;\Leftrightarrow\; f(x_1) = f(x_2).$
  Thus we have $[x] = \set{x' \in X \;\big|\; f(x) = f(x')}$.
